NumPy---Array Computation for Python

### 2020-01-09 body.tex
Add some notes

@@

@@

Over the last decade, NumPy has attracted more scientist developers.
The project has strong culture of using software-engineering practice to
improve collaboration and reduce error \cite{millman2014developing}.
The NumPy team was early in adopting distributed
revision control and code review to improve collaboration on code, and
continuous testing that runs a large battery of automated tests for every proposed
change to NumPy.
The project has comprehensive, high-quality documentation,
integrated with the source
code\cite{vanderwalt2008scipy,harrington2008scipy,harrington2009scipy}.

@@

Hugunin identified the first factor in his initial description of the Numeric
package \cite{Hugunin-whitepaper}.  Numerical computing is usually one
component of a larger programming task, therefore:

\begin{quote}
    Rather than trying to retrofit an existing numerical language to support
    the wealth of features found in a powerful, modern, general-purpose
    programming language, it makes much more sense to attack the problem from
    the other direction and add the features of a powerful numerical
    programming language to Python.
\end{quote}

Python is already a good choice for many standard programming tasks such as
cleaning data, interacting with web resources and parsing text.  It has a wide
range of libraries for many different tasks. Adding fast array operations and
linear algebra allows the scientist to do all their work with within the same
language---and one that has the advantage of being famously easy to learn and
teach.

@@

The third factor is much like the second: a culture in Python that concentrates
on high quality of code and distribution. Because Python is open-source, it has
a strong culture of contribution, and therefore, of using tools and process to
improve collaborative software development, such as distributed version
control, code review, and automated testing.  These have allowed the project to
scale safely as it attracted more users and developers, even though these
developers rarely came to the project with training in software engineering.

>>>>

\fixme{The idea here is something like:  classic numpy (as described above)
was built to solve previous problems; new problems have arisen as
the computational landscape has changed; new hardware, new languages,
new problems; as a result np's role has changed; it is a foundational
tool widely-used not a specialist tool used by scientist developers;
many array-like libraries for various uses and np is serving as
a standard)}

@@

% https://numpy.org/neps/nep-0016-abstract-array.html
% https://numpy.org/neps/nep-0018-array-function-protocol.html
% https://numpy.org/neps/nep-0022-ndarray-duck-typing-overview.html
% https://numpy.org/neps/nep-0030-duck-array-protocol.html
% https://numpy.org/neps/nep-0037-array-module.html

@@

@@

Hugunin identified the first factor in his initial description of the Numeric
package \cite{Hugunin-whitepaper}.  Numerical computing is usually one
component of a larger programming task, therefore:
\begin{quote}
    Rather than trying to retrofit an existing numerical language to support
    the wealth of features found in a powerful, modern, general-purpose
    programming language, it makes much more sense to attack the problem from
    the other direction and add the features of a powerful numerical
    programming language to Python.
\end{quote}
Python is already a good choice for many standard programming tasks such as
cleaning data, interacting with web resources and parsing text.  It has a wide
range of libraries for many different tasks. Adding fast array operations and
linear algebra allows the scientist to do all their work with within the same
language---and one that has the advantage of being famously easy to learn and
teach.

@@

The third factor is much like the second: 
%a culture in Python that concentrates
%on high quality of code and distribution.  Because Python is open-source, it has
%a strong culture of contribution, and therefore, of using tools and process to
%improve collaborative software development, such as distributed version
%control, code review, and automated testing.  These have allowed the project to
%scale safely as it attracted more users and developers, even though these
%developers rarely came to the project with training in software engineering.
the project has strong culture of using software-engineering practice to
improve collaboration and reduce error \cite{millman2014developing}.
The NumPy team was early in adopting distributed
revision control and code review to improve collaboration on code, and
continuous testing that runs a large battery of automated tests for every proposed
change to NumPy.
The project has comprehensive, high-quality documentation,
integrated with the source
code\cite{vanderwalt2008scipy,harrington2008scipy,harrington2009scipy}.
